---
title: "AirPollution"
author: "Linda Lee"
date: "2019/7/11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Subject
Is PM2.5/AQI related to "restaurant" ?
<br>Show the restaurants 5km around the site station, and view that site's AQI (Air Quality Index).
<br>We want to find out any clues then get the result, well we might not get the answer but we can learn something from this study.

## DataSet

* [餐飲 - 觀光資訊資料庫](https://data.gov.tw/dataset/7779)
    + Download .xml
    + Conver to .csv
    + online tool : [XML To CSV Converter](http://www.convertcsv.com/xml-to-csv.htm)

    
* [空氣品質監測站經緯度](https://erdb.epa.gov.tw/DataRepository/Facilities/AirQualityMonitorStations.aspx?topic1=%E8%A8%AD%E6%96%BD&topic2=%E5%A4%A7%E6%B0%A3&subject=%E6%B8%AC%E7%AB%99)
    + Download .csv
    + Rename the field name(column) from Chinese to English
    
     | 序號   |縣市 |鄉鎮市區 |測站名稱 |測站地址 |空品區   |經度     |緯度     |影像連結 |
     |--------|------|--------|---------|---------|---------|---------|---------|---------|
     | Number |City |Zone     |Name     |Address  |AreaZone |Longitud |Latitude |ImageLink|
     


## Reference

* （https://wywu.pixnet.net/blog/post/22338038-台灣地區經緯度的距離)
    + 西  1度 101751.561277 M
    + 東  1度 101751.561277 M
    + 南  1度 110751.075273 M
    + 北  1度 110765.515243 M
  

## R
### 讀入資料
```{r}
library(dplyr)
restaurantfile <- "/Users/linda/Desktop/CS+X-108/20190711/convertcsv.csv"

restaurantdata_raw<-read.csv(restaurantfile, header=T, sep=",")
dim(restaurantdata_raw)
head(restaurantdata_raw)
```
### 讀檔名是中文的資料檔,下述方法不成功<br>
|sitefile <- "/Users/linda/Desktop/CS+X-108/20190711/空氣品質監測站Eng.csv"                                   |
|-------------------------------------------------------------------------------------------------------------|
|sitedata<-read.csv(sitefile, header=T, sep=",")  # failed to read like this since the file name is in Chinese|

### 改成直接寫在function內
```{r}
sitedata_raw<-read.csv("/Users/linda/Desktop/CS+X-108/20190711/空氣品質監測站Eng.csv", header=T, sep=",")
dim(sitedata_raw)
head(sitedata_raw)
```
### 處理[資料集]Site:含欄位
```{r}
#--------------- [DataSet] Site ---------------
sitedata <- select(sitedata_raw, Name, Longitude,Latitude)
sitedata = sitedata[sitedata$Name != "",]    # remove empty row
dim(sitedata)
sitedata$Name <- paste(sitedata$Name,"Site", sep="_")   #append "Site" to each $Name
#head(sitedata)

# rename the specified columns' name 
names(sitedata)[names(sitedata) == "Longitude"] <- "Px"
names(sitedata)[names(sitedata) == "Latitude"] <- "Py"
# add a column - "Description"
Description=""
sitedata = cbind(sitedata, Description)
head(sitedata)
dim(sitedata)
```
### 處理[資料集]Restaurant:含欄位
```{r}
#--------------- [DataSet] Restaurant ---------------
restaurantdata <- select(restaurantdata_raw, Name, Px, Py, Description)
head(restaurantdata)
dim(restaurantdata)
```
### 合併資料集
```{r}
# merge [sie], [restaurant]
data = rbind(restaurantdata, sitedata)
dim(data)
library(kableExtra)
kable(head(data))
```


